Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code

### 2015-10-21 fib2.tex
more words

This is not at all the case in general;
for non-Abelian theories there can be extra
degrees of freedom associated with these
observables. For example, in
the Fibonacci anyon case
\begin{center}
\includegraphics[]{pic-fusion.pdf}
\end{center}
so the state space of two fibonacci anyons
is $2$-dimensional.
Such a space assocated with observing total charge
of multiple anyons is called the \emph{fusion} space
of those charges.

@@

The basic data structure involved in the
simulation we term a \emph{combinatorial curve
diagram.}
For each cell in the lattice,
we store a combinatorial
description of the curve intersected with that cell.
This will be insensitive to any continuous deformation of the interior of the cell,
but the simulation does not need to track any of these degrees of freedom.
\begin{center}
\includegraphics[]{pic-cells.pdf}
\end{center}
We follow essentially the same approach as taken in \cite{Abramsky2007} 
to describe elements of a Temperley-Leib algebra, but
with some extra decorations.
The key idea is to store a \emph{word} for each cell, comprised of
the letters $<$ and $>$.
When these brackets are balanced,
each such word will correspond one-to-one with an intersection
of a curve in a cell (up to any continuous deformation of the interior of the cell).
The encoding works as follows.
Reading in a clockwise direction around the edge of
the cell from the top-left corner,
we record our encouters with each piece of curve diagram,
writing a $<$ for the first encounter, and $>$ for the
second. We may also encounter a dangling piece of curve
diagram (the head or the tail), so we use another symbol $*$ for this.
The words for the above two cells will then be $<<>><>$ and $<>*<<>>.$
Getting more elaborate, we will also need to record the direction
of each piece of curve,
and we allow anyons to reside on the curve
close to the edge. (This means we cannot have more than two anyons
per piece, but if that is needed we will have added another curve diagram.)
We will also record,
for each intersection with the cell edge, which side the
intersection occurs on.

Various other consistency relations are enforced on a combinatorial curve diagram,
such as requiring two
adjacent cells to agree on their boundaries, and every curve diagram
having two ends.
(Note that in general we will have many disjoint curve diagrams.)
We also require every curve diagram to intersect 
the edges of cells transversally.
This will mean in particular that a curve will not touch a cell corner.

Two disjoint curves can be joined by...

Curves can be simplified along sections without any anyons, ...

>>>>

This is not at all the case in general;
for non-Abelian theories there can be extra
degrees of freedom associated with these
observables. For example, in
a system supporting Fibonacci anyons,
we can have two Fibonacci anyons with total
charge either vacuum or Fibonacci:
\begin{center}
\includegraphics[]{pic-fusion.pdf}
\end{center}
so the state space of two fibonacci anyons
is $2$-dimensional.
Such a space assocated with observing total charge
of multiple anyons is called the \emph{fusion} space
of those charges.

@@

The basic data structure involved in the
simulation we term a \emph{combinatorial curve
diagram.}
For each cell in the lattice,
we store a combinatorial
description of the curve(s) intersected with that cell.
This data structure 
will be insensitive to any continuous deformation of the interior of the cell,
but the simulation does not need to track any of these degrees of freedom.
\begin{center}
\includegraphics[]{pic-cells.pdf}
\end{center}
We follow essentially the same approach as taken in \cite{Abramsky2007} 
to describe elements of a Temperley-Leib algebra, but
with some extra decorations.
The key idea is to store a \emph{word} for each cell, comprised of
the letters $\bigl<$ and $\bigr>$.
When these brackets are balanced,
each such word will correspond one-to-one with an intersection
of a curve in a cell (up to any continuous deformation of the interior of the cell).
The encoding works as follows.
Reading in a clockwise direction around the edge of
the cell from the top-left corner,
we record our encounters with each piece of curve diagram,
writing~$\bigl<$ for the first encounter, and~$\bigr>$ for the
second. We may also encounter a dangling piece of curve
diagram (the head or the tail), so we use another symbol $*$ for this.
The words for the above two cells will then be 
$\bigl<\bigl<\bigr>\bigr>\bigl<\bigr>$ and $\bigl<\bigr>*\bigl<\bigl<\bigr>\bigr>.$

We will also need to record
various other attributes of these curves,
and to do this we make this notation more elaborate
in the paragraphs {\bf (I)}, {\bf(II)} and {\bf(III)} below.
Each symbol in the word describes an intersection of
the curve with the cell boundary,
and so as we decorate these symbols these decorations will
apply to such intersection points.

{\bf (I)} We will record the direction of each piece of curve,
this will be either an {\tt in} or {\tt out} decoration for each symbol.
Such decorations need to balance according to the brackets,
eg. $\bigl<_{\mbox{\tt in}}\bigl<_{\mbox{\tt out}}\bigr>_{\mbox{\tt in}}\bigr>_{\mbox{\tt out}}\bigl<_{\mbox{\tt out}}\bigr>_{\mbox{\tt in}}$.
Similarly, the decorated symbols $*_{\mbox{\tt in}}$ and 
$*_{\mbox{\tt out}}$ 
will denote respectively either
the head, $c(1)$ or the tail $c(0)$ of a curve.

{\bf (II)} We will record,
for each intersection with the cell edge, which of the four
sides of the cell the
intersection occurs on.
Numbering these clockwise from the top as $1, 2, 3, 4$ we have for the above curves: 
$\bigl<_1\bigl<_2\bigr>_2\bigr>_3\bigl<_3\bigr>_4$ 
and $\bigl<_1\bigr>_1*_2\bigl<_3\bigl<_3\bigr>_4\bigr>_4.$
This will require every curve diagram to intersect 
the edges of cells transversally,
and in particular a curve will not touch a cell corner.

{\bf (III)} Finally, we will also decorate these symbols with anyons.
This will be an index to a leaf of a (sum of) fusion tree(s).
This means that anyons only reside on the curve close
to the cell boundary,
and so we cannot have more than two anyons
for each piece of curve. 
The number of such pieces is arbitrary, and so this
is no restriction on generality.

Various other consistency relations are enforced on such a combinatorial curve diagram,
such as requiring two
adjacent cells to agree on their boundaries, and every curve diagram
having two ends.
(Note that in general we will have many disjoint curve diagrams.)

%Two disjoint curves can be joined by...
%
%Curves can be simplified along sections without any anyons, ...
